### 2019-06-05 doc/chapters/trying_verify_checktx.tex
added ref
changed title
fixed foot note

This was fixed in pull request \mypound435 on GitHub\footnote{https://github.com/bitcoin-s/bitcoin-s/pull/435} at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.

\section{Process of Verification // TODO change}

Trying to integrate Stainless in Bitcoin-S caused a lot of troubles, because of version conflicts.
If you are interested in it you can read \hl{TODO} in the appendix.

>>>>

This was fixed in pull request \mypound435 on GitHub\footnote{\url{https://github.com/bitcoin-s/bitcoin-s/pull/435}} at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.

\section{Adjusting Property}

Trying to integrate Stainless in Bitcoin-S caused a lot of troubles, because of version conflicts.
If you are interested in it you can read more in the appendix \ref{chap:appendix_arb}.
